---
title: "1.2020 CSHL Epigenetics & Chromatin"
description: 
icon: ti-upload
# type: docs
draft: false
date: 2020-08-20T11:02:05+06:00
lastmod: 2020-08-22T10:42:26+06:00
weight: 1
output:
  html_document:
    keep_md: yes
---

#### The Meeting Info:


+ Meeting - 1

Title: 2020 CSHL Epigenetics & Chromatin

Date: September 15 - 18 2020 Virtual    

The official [website](https://meetings.cshl.edu/meetings.aspx?meet=EPICH&year=20), and the meeting [Program](http://159.226.118.232/upload/img/2020_CSHL_videos/2020-CSHL-Epigenitics-Chromatin-meeting-program.pdf) - saved on Yulab Cloud. Here are the meeting [Abstract](http://159.226.118.232/upload/img/2020_CSHL_videos/2020-CSHL-Epigenitics-Chromatin-Abstract.pdf)


+ Meeting - 2

Title: 

Date: 

The official [website]()


#### Video list

Here is the full table of the videos [2020-CSHL-Genetics-list.xlsx](2020-CSHL-Genetics-list.xlsx)


```{r, echo = FALSE}
suppressPackageStartupMessages(library(DT))
suppressPackageStartupMessages(library(dplyr))

# read list
flist <- "2020-CSHL-Genetics-list.xlsx"
vlist <- readxl::read_xlsx(flist, sheet = "Sheet1")

# Reading the video list
baseurl <- "http://159.226.118.232/upload/img/2020_CSHL_videos"

df <- vlist %>%
  tidyr::separate(filename, c("group", "fname"), sep = "/") %>%
  dplyr::mutate(title = ifelse(title == "T.I.", fname, title),
                url   = file.path(baseurl, group, fname),
                link  = paste0("<a href='", url, "' target='_blank'>", title, "</a>") ) %>%
  tibble::rowid_to_column("Count") %>%
  dplyr::select(count, speaker, link, group)
  
# 20200916
df1 <- df %>%
  filter(group %in% c("20200916")) %>%
  dplyr::select(-group)
  
# 20201001
df2 <- df %>%
  filter(group %in% c("20201001")) %>%
  dplyr::select(-group)

# 20201002
df3 <- df %>%
  filter(group %in% c("20201002")) %>%
  dplyr::select(-group)

# 20201008
df4 <- df %>%
  filter(group %in% c("20201008")) %>%
  dplyr::select(-group)

# 20201009
df5 <- df %>%
  filter(group %in% c("20201009")) %>%
  dplyr::select(-group)

# 20201010
df6 <- df %>%
  filter(group %in% c("20201010")) %>%
  dplyr::select(-group)

# 20201124, for chenkai
df7 <- df %>%
  filter(group %in% c("for_chenkai")) %>%
  dplyr::select(-group)

```


#### part1: 2020-09-16 uploaded

```{r, echo = FALSE}
knitr::kable(df1)
```


#### part2: 2020-10-01 uploaded

```{r, echo = FALSE}
knitr::kable(df2)
```



#### part3: 2020-10-02 uploaded

```{r, echo = FALSE}
knitr::kable(df3)
```

#### part4: 2020-10-08 uploaded

```{r, echo = FALSE}
knitr::kable(df4)
```


#### part5: 2020-10-09 uploaded

```{r, echo = FALSE}
knitr::kable(df5)
```

#### part6: 2020-10-10 uploaded

```{r, echo = FALSE}
knitr::kable(df6)
```



#### part7: 2020-11-24 uploaded (for ChenKai)

```{r, echo = FALSE}
knitr::kable(df7)
```


<!-- + 01  -->

<!-- <video width="640" height="480" controls> -->
<!--   <source src="http://159.226.118.232/upload/img/2020_CSHL_videos/VID_20200916_223943.mp4" type="video/mp4"> -->
<!--   Your browser does not support the video tag. -->
<!-- </video> -->

<!-- + 02 -->

<!-- <video width="640" height="480" controls> -->
<!--   <source src="http://159.226.118.232/upload/img/2020_CSHL_videos/VID_20200916_225521.mp4" type="video/mp4"> -->
<!--   Your browser does not support the video tag. -->
<!-- </video> -->

<!-- + 03 -->

<!-- <video width="640" height="480" controls> -->
<!--   <source src="http://159.226.118.232/upload/img/2020_CSHL_videos/VID_20200916_231616.mp4" type="video/mp4"> -->
<!--   Your browser does not support the video tag. -->
<!-- </video> -->

<!-- + 04 -->

<!-- <video width="640" height="480" controls> -->
<!--   <source src="http://159.226.118.232/upload/img/2020_CSHL_videos/VID_20200916_233123.mp4" type="video/mp4"> -->
<!--   Your browser does not support the video tag. -->
<!-- </video> -->

<!-- + 05  -->

<!-- <video width="640" height="480" controls> -->
<!--   <source src="http://159.226.118.232/upload/img/2020_CSHL_videos/VID_20200917_001413.mp4" type="video/mp4"> -->
<!--   Your browser does not support the video tag. -->
<!-- </video> -->

<!-- + 06 -->

<!-- <video width="640" height="480" controls> -->
<!--   <source src="http://159.226.118.232/upload/img/2020_CSHL_videos/VID_20200917_221721.mp4" type="video/mp4"> -->
<!--   Your browser does not support the video tag. -->
<!-- </video> -->

<!-- + 07  -->

<!-- <video width="640" height="480" controls> -->
<!--   <source src="http://159.226.118.232/upload/img/2020_CSHL_videos/VID_20200917_223259.mp4" type="video/mp4"> -->
<!--   Your browser does not support the video tag. -->
<!-- </video> -->

<!-- + 08 -->

<!-- <video width="640" height="480" controls> -->
<!--   <source src="http://159.226.118.232/upload/img/2020_CSHL_videos/VID_20200917_225112.mp4" type="video/mp4"> -->
<!--   <track label="English" kind="subtitles" srclang="en" src="http://159.226.118.232/upload/img/2020_CSHL_videos/Susan-Gasser-2020-MCB.vtt" default> -->
<!--   Your browser does not support the video tag. -->
<!-- </video> -->

<!-- + 09 -->

<!-- <video width="640" height="480" controls> -->
<!--   <source src="http://159.226.118.232/upload/img/2020_CSHL_videos/VID_20200917_230859.mp4" type="video/mp4"> -->
<!--   <track label="English" kind="subtitles" srclang="en" src="http://159.226.118.232/upload/img/2020_CSHL_videos/Susan-Gasser-2020-MCB.vtt" default> -->
<!--   Your browser does not support the video tag. -->
<!-- </video> -->

<!-- + 10  -->

<!-- <video width="640" height="480" controls> -->
<!--   <source src="http://159.226.118.232/upload/img/2020_CSHL_videos/VID_20200917_232510.mp4" type="video/mp4"> -->
<!--   <track label="English" kind="subtitles" srclang="en" src="http://159.226.118.232/upload/img/2020_CSHL_videos/Susan-Gasser-2020-MCB.vtt" default> -->
<!--   Your browser does not support the video tag. -->
<!-- </video> -->

