---
title: "1. 2020 CSHL Epigenetics & Chromatin"
description: 
icon: ti-upload
# type: docs
draft: false
date: 2020-08-20T11:02:05+06:00
lastmod: 2020-08-22T10:42:26+06:00
weight: 1
---

<!--
### Videos on Yulab Cloud

~[Click here](http://192.168.206.171/yulab_cloud/index.php/s/XaDaxZFb2c6Pbk9), find the videos uploaded by Yu and Yuan.~ 

~~Click here, find the videos uploaded by Yu and Yuan~~ [本链接已失效，请改用FTP工具上传，详情咨询课题组微信群]

-->


### Meeting

September 15 - 18 2020 Virtual    
Abstract Deadline: June 26, 2020    

The official [website](https://meetings.cshl.edu/meetings.aspx?meet=EPICH&year=20)    

The meeting [Program](http://159.226.118.232/upload/img/2020_CSHL_videos/2020-CSHL-Epigenitics-Chromatin-meeting-program.pdf) - saved on Yulab Cloud.      

The meeting [Abstract](http://159.226.118.232/upload/img/2020_CSHL_videos/2020-CSHL-Epigenitics-Chromatin-Abstract.pdf)

Organizers:

Anja Groth, CPR, University of Copenhagen, Denmark  

Kristian Helin, Memorial Sloan Kettering Cancer Center

Yang Shi, Harvard Medical School

### Highlight: 

+ [Susan Gasser](/yulab_share/post/2020_cshl_epigenetics_and_chromatin/susan_gasser/) - Friedrich Miescher Institute for Biomedical Research, Switzerland

### 2020 CSHL videos 

```{r, echo = FALSE}
suppressPackageStartupMessages(library(DT))
suppressPackageStartupMessages(library(dplyr))

# Reading the video list
baseurl <- "http://159.226.118.232/upload/img/2020_CSHL_videos"
vlist <- readLines("./video_list.txt")
df    <- data.frame(group = dirname(vlist),
                    fname = basename(vlist),
                    url   = file.path(baseurl, vlist), 
                    note  = "leave a note here") %>%
  mutate(link = paste0("<a href='", url, "' target='_blank'>", fname, "</a>"))
  
# 20200916
df1 <- df %>%
  filter(group %in% c("20200916")) %>%
  dplyr::select(link, note)
  
# 20201001
df2 <- df %>%
  filter(group %in% c("20201001")) %>%
  dplyr::select(link, note)

# 20201002
df3 <- df %>%
  filter(group %in% c("20201002")) %>%
  dplyr::select(link, note)
```

#### part1: 2020-09-16 uploaded

```{r, echo = FALSE}
DT::datatable(df1, escape = FALSE, options = list(
  pageLength = 40,
  dom = "tlp"
))
```

#### part2: 2020-10-01 uploaded

```{r, echo = FALSE}
DT::datatable(df2, escape = FALSE, options = list(
  pageLength = 40,
  dom = "tlp"
))
```


#### part3: 2020-10-02 uploaded

```{r, echo = FALSE}
DT::datatable(df3, escape = FALSE, options = list(
  pageLength = 40,
  dom = "tlp"
))
```



<!-- + 01  -->

<!-- <video width="640" height="480" controls> -->
<!--   <source src="http://159.226.118.232/upload/img/2020_CSHL_videos/VID_20200916_223943.mp4" type="video/mp4"> -->
<!--   Your browser does not support the video tag. -->
<!-- </video> -->

<!-- + 02 -->

<!-- <video width="640" height="480" controls> -->
<!--   <source src="http://159.226.118.232/upload/img/2020_CSHL_videos/VID_20200916_225521.mp4" type="video/mp4"> -->
<!--   Your browser does not support the video tag. -->
<!-- </video> -->

<!-- + 03 -->

<!-- <video width="640" height="480" controls> -->
<!--   <source src="http://159.226.118.232/upload/img/2020_CSHL_videos/VID_20200916_231616.mp4" type="video/mp4"> -->
<!--   Your browser does not support the video tag. -->
<!-- </video> -->

<!-- + 04 -->

<!-- <video width="640" height="480" controls> -->
<!--   <source src="http://159.226.118.232/upload/img/2020_CSHL_videos/VID_20200916_233123.mp4" type="video/mp4"> -->
<!--   Your browser does not support the video tag. -->
<!-- </video> -->

<!-- + 05  -->

<!-- <video width="640" height="480" controls> -->
<!--   <source src="http://159.226.118.232/upload/img/2020_CSHL_videos/VID_20200917_001413.mp4" type="video/mp4"> -->
<!--   Your browser does not support the video tag. -->
<!-- </video> -->

<!-- + 06 -->

<!-- <video width="640" height="480" controls> -->
<!--   <source src="http://159.226.118.232/upload/img/2020_CSHL_videos/VID_20200917_221721.mp4" type="video/mp4"> -->
<!--   Your browser does not support the video tag. -->
<!-- </video> -->

<!-- + 07  -->

<!-- <video width="640" height="480" controls> -->
<!--   <source src="http://159.226.118.232/upload/img/2020_CSHL_videos/VID_20200917_223259.mp4" type="video/mp4"> -->
<!--   Your browser does not support the video tag. -->
<!-- </video> -->

<!-- + 08 -->

<!-- <video width="640" height="480" controls> -->
<!--   <source src="http://159.226.118.232/upload/img/2020_CSHL_videos/VID_20200917_225112.mp4" type="video/mp4"> -->
<!--   <track label="English" kind="subtitles" srclang="en" src="http://159.226.118.232/upload/img/2020_CSHL_videos/Susan-Gasser-2020-MCB.vtt" default> -->
<!--   Your browser does not support the video tag. -->
<!-- </video> -->

<!-- + 09 -->

<!-- <video width="640" height="480" controls> -->
<!--   <source src="http://159.226.118.232/upload/img/2020_CSHL_videos/VID_20200917_230859.mp4" type="video/mp4"> -->
<!--   <track label="English" kind="subtitles" srclang="en" src="http://159.226.118.232/upload/img/2020_CSHL_videos/Susan-Gasser-2020-MCB.vtt" default> -->
<!--   Your browser does not support the video tag. -->
<!-- </video> -->

<!-- + 10  -->

<!-- <video width="640" height="480" controls> -->
<!--   <source src="http://159.226.118.232/upload/img/2020_CSHL_videos/VID_20200917_232510.mp4" type="video/mp4"> -->
<!--   <track label="English" kind="subtitles" srclang="en" src="http://159.226.118.232/upload/img/2020_CSHL_videos/Susan-Gasser-2020-MCB.vtt" default> -->
<!--   Your browser does not support the video tag. -->
<!-- </video> -->

